Inefficient Concessions and Mediation

### 2020-12-14 notes.tex
fix max calculations in R script; add results from R to notes

\vskip.3in
``Parameterization 2'': goal was to make welfare higher under mediator
\begin{itemize}
	\item \color{orange} T = 7, W = 8, D = 5, p = .9, $\de_l = .3$, $\de_h = .6$
	\item Minimum $e$ from Expression~\ref{eq:g6}
	  $$0.9 - \frac{\left(1 - 0.3 \right) \left( 7 + 5 \right)}{g} \geq e \left( 0.9 + 7 - 0.3 \cdot 7 + 8 \right)$$
		$$0.9 - \frac{8.4}{g} \geq e \left(18 \right)$$
		$$0.05 - \frac{0.466}{g} \geq e $$
	\item The highest welfare comes from $e=.06$, which implies $g = 116.67$ (see e-g calculations.R)

\end{itemize}

						\vskip.3in
						Welfare comparisons (always for high type)
							\begin{itemize}
								\item When $e=1$: $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$
									\begin{itemize}
										\item \color{red} Parameterization in the paper: welfare is 7.18; gift is 0.63
										\item \color{orange} Parameterization 2: $g1$ is negative, creates negative upper bound for $d_h$. Separating with concessions equilibrium can't be sustained.
									\end{itemize}
								\item When $e=0$: $\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$
									\begin{itemize}
										\item \color{red} Parameterization in the paper: welfare is 8; gift is 3
										\item \color{orange} Parameterization 2: welfare is 5.7; gift is 10.8
									\end{itemize}
								\item When $0<e<1$ under a mediator: $\frac{1}{1-d_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - g_M$
									\begin{itemize}
										\item Optimal $g_M$: Expression~\ref{eq:g2} creates a menu of $(e,g)$ pairs that satisfy the constraint:
											\[
												g_M \geq \frac{\left(1 - \de \right) \left( T + D \right)}{p - e \left( p + T - \de T + W \right)}
											\]
										\item We're assuming $p - e \left( p + T - \de T + W \right) > 0$ (assuming gifts must be non-negative)
										\item Also $pg - \left(1 - \de \right) \left( T + D \right) \geq 0$ ($e$ version; this is WEAKER than the condition on $e$)
										\item \color{red} For the parameterization in the paper, welfare is negative for $e=0$ and $e=0.01$, the only values of $e$ that lead to non-negative gifts; gifts range from 52.5 to 218.75	
										\item \color{orange} Parameterization 2: welfare is 10.083 at optimal gift-efficiency $e=0.06$, $g = 116.67$, $eg = 7$
											\begin{itemize}
												\item Compared to $e=0$, welfare (gross of gift) goes up from 16.5 to 126.75. The entire difference is due to the positive effect of the material value of the gift (the full term is $\frac{1}{1-\de_h}pTeg$). The effective gift is $7$, which is much larger than the 1 in $\frac{1}{1-\de_h}pT\cdot 1$ that is there in both terms.
												\item The increase in the size (cost) of the gift from 10.8 to 116.67 is smaller than the increase in gross-of-gift welfare
											\end{itemize}
									\end{itemize}
							\end{itemize}

>>>>

\vskip.3in
``Parameterization 2'': goal was to make welfare higher under mediator; $We > W0$ and $e=1$ is not incentive compatible
\begin{itemize}
	\item \color{orange} T = 7, W = 8, D = 5, p = .9, $\de_l = .3$, $\de_h = .6$
	\item Minimum $e$ from Expression~\ref{eq:g6}
	  $$0.9 - \frac{\left(1 - 0.3 \right) \left( 7 + 5 \right)}{g} \geq e \left( 0.9 + 7 - 0.3 \cdot 7 + 8 \right)$$
		$$0.9 - \frac{8.4}{g} \geq e \left(18 \right)$$
		$$0.05 - \frac{0.466}{g} \geq e $$
	\item The highest welfare comes from $e=.06$, which implies $g = 116.67$ (see e-g calculations.R)
\end{itemize}

\vskip.3in
Here $W1 > W0$ and $g1 > g0$. Welfare under mediator is never positive. 
\begin{itemize}
	\item T = 7, W = 8, D = 5, p = .5, dl = .25, dh = .6
\end{itemize}

\vskip.3in
Here, $W0 > W1 > We$ (mediator). Mediator optimally chooses e=0 anyway
\begin{itemize}
	\item T = 7, W = 8, D = 5, p = .3, dl = .4, dh = .9
\end{itemize}

\vskip.3in
Here, $W0 > W1 > We$ (mediator). Mediator optimally chooses $e=0.03$
\begin{itemize}
	\item T = 6, W = 8, D = 5, p = .5, dl = .2, dh = .9
\end{itemize}

						\vskip.3in
						Welfare comparisons (always for high type)
							\begin{itemize}
								\item When $e=1$: $\frac{1}{1-d_h}\left\{pT(1+g^*) + (1-p)(W-D(1+g^*))\right\} - \frac{p(1-d_l)(D+T)}{(1-d_l)(1-pT)+(1-p)D}$
									\begin{itemize}
										\item \color{red} Parameterization in the paper: welfare is 7.18; gift is 0.63
										\item \color{orange} Parameterization 2: $g^1$ is negative, creates negative upper bound for $d_h$. Separating with concessions equilibrium can't be sustained.
									\end{itemize}
								\item When $e=0$: $\frac{1}{1-d_h}\left\{pT + (1-p)(W-D)\right\} - p(T+D)$
									\begin{itemize}
										\item \color{red} Parameterization in the paper: welfare is 8; gift is 3
										\item \color{orange} Parameterization 2: welfare is 5.7; gift is 10.8
									\end{itemize}
								\item When $0<e<1$ under a mediator: $\frac{1}{1-d_h}\left\{pT(1+eg_M) + (1-p)(W-D)\right\} - g_M$
									\begin{itemize}
										\item Optimal $g_M$: Expression~\ref{eq:g2} creates a menu of $(e,g)$ pairs that satisfy the constraint:
											\[
												g_M \geq \frac{\left(1 - \de \right) \left( T + D \right)}{p - e \left( p + T - \de T + W \right)}
											\]
										\item We're assuming $p - e \left( p + T - \de T + W \right) > 0$ (assuming gifts must be non-negative)
										\item Also $pg - \left(1 - \de \right) \left( T + D \right) \geq 0$ ($e$ version; this is WEAKER than the condition on $e$)
										\item \color{red} For the parameterization in the paper, welfare is negative for $e=0$ and $e=0.01$, the only values of $e$ that lead to non-negative gifts; gifts range from 52.5 to 218.75	
										\item \color{orange} Parameterization 2: welfare is 10.083 at optimal gift-efficiency $e=0.06$, $g = 116.67$, $eg = 7$
											\begin{itemize}
												\item Compared to $e=0$, welfare (gross of gift) goes up from 16.5 to 126.75. The entire difference is due to the positive effect of the material value of the gift (the full term is $\frac{1}{1-\de_h}pTeg$). The effective gift is $7$, which is much larger than the 1 in $\frac{1}{1-\de_h}pT\cdot 1$ that is there in both terms.
												\item The increase in the size (cost) of the gift from 10.8 to 116.67 is smaller than the increase in gross-of-gift welfare
											\end{itemize}
									\end{itemize}
							\end{itemize}
